### 2017-02-27 draft-md-ct.tex
a question

@@

Now, for a fixed arbitrary $x$, we get
\begin{align*}
\sum_{k=1}^{t} \ab{v_{k},x}
= \int_{0}^{t} \ab{v(s), x} ds 
&\leq \int_{0}^{t} \ab{v(s), x(s)} ds + \frac{R_{\text{max}} - R_{\text{min}}}{\eta} \\
&\leq \sum_{k=1}^{t} \ab{v_{k},x_{k}} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2 
     + \frac{R_{\text{max}} - R_{\text{min}}}{\eta}\,.
\end{align*}
The first inequality is from \eqref{eq.cta.bound} and the second inequality
from the above continuous/discrete time comparison for the linearized losses.
Finally, using linearization of the original losses (in discrete time) we get
\begin{align*}
\sum_{k=1}^{t} \ell_{k}(x_{k}) - \sum_{k=1}^{t} \ell_{k}(x)
&\leq \sum_{k=1}^{t} \ab{v_{k},x - x_{k}} \\
&\leq \frac{R_{\text{max}} - R_{\text{min}}}{\eta} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2\,.
\end{align*}

>>>>

\usepackage[textsize=tiny]{todonotes}
\setlength{\marginparwidth}{15ex}
\newcommand{\todoc}[2][]{\todo[size=\scriptsize,color=blue!20!white,#1]{Csaba: #2}}
\newcommand{\todoo}[2][]{\todo[size=\scriptsize,color=red!20!white,#1]{Omar: #2}}

@@

Now, for a fixed arbitrary $x$, we get
\begin{align*}
\sum_{k=1}^{t} \ab{v_{k},x}
= \int_{0}^{t} \ab{v(s), x} ds 
&\leq \int_{0}^{t} \ab{v(s), x(s)} ds + \frac{R_{\text{max}} - R_{\text{min}}}{\eta} \\
&\leq \sum_{k=1}^{t} \ab{v_{k},x_{k}} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2 
     + \frac{R_{\text{max}} - R_{\text{min}}}{\eta}\,.
\end{align*}
The first inequality is from \eqref{eq.cta.bound} \todoc{Why can this be applied?
Does $(x(t),y(t))_{t}$ satisfy \eqref{eq.cta.1}--\eqref{eq.cta.2}? Any other conditions?}
and the second inequality
from the above continuous/discrete time comparison for the linearized losses.
Finally, using linearization of the original losses (in discrete time) we get
\begin{align*}
\sum_{k=1}^{t} \ell_{k}(x_{k}) - \sum_{k=1}^{t} \ell_{k}(x)
&\leq \sum_{k=1}^{t} \ab{v_{k},x - x_{k}} \\
&\leq \frac{R_{\text{max}} - R_{\text{min}}}{\eta} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2\,.
\end{align*}
